### 2019-09-30 uiuc.tex
adds advisor letter, fixes headheight which was squashing the page numbers, and adds some more text for a couple of missing labs. Finally, adds faculty photos

\subsection{Research at UIUC}
Faculty and students in NPRE conduct research in many areas of interest to the nuclear science community. Both graduate and undergraduate  students actively participate and make their own atomic contributions that will someday save the world.

@@

\subsubsection{NPRE Research Groups and Laboratories}
\begin{itemize}
  \item \textbf{Advanced Reactors and Fuel Cycles (ARFC)} - \textit{Dr. Kathryn Huff}\\
  The ARFC group seeks to advance the safety and sustainability of nuclear energy production through improved reactor designs, fuel cycle strategies, and waste management techniques. In the area of advanced reactors, our work focuses on extending current simulation tools with features essential to advanced reactor multiphysics. In the context of the broader nuclear fuel cycle, the ARFC group emphasizes modeling, simulation, and analysis of the global nuclear fuel cycle, with an emphasis on sustainability. A crosscutting theme of our research is an emphasis on advancing methods and software for computational nuclear engineering. Accordingly, the Advanced Reactors and Fuel Cycles group is proud to be affiliated with the University of Illinois National Center for Supercomputing Applications and its Blue Waters computing facility.
  \item \textbf{Virtual Education and Research Laboratory (VERL)} - \textit{Dr. Rizwan Uddin}\\
  The VERL group focuses on the development of innovative numerical methods and their implementation on high performance computing machines. Research efforts center on problems in nuclear engineering, with emphasis on thermal-hydraulics and reactor physics.

@@

  \item \textbf{Laboratory: Multiphase Thermo-fluid Dynamics Lab} - \textit{Dr. Caleb Brooks}\\
  This group performs experiments related to thermal hydraulics and multiphase flow. Phenomena studied include boiling, condensation, critical heat flux, natural circulation, two-phase flow instabilities, bubble dynamics, and two-phase transport. Utilizing advanced instrumentation, data from these experiments are used in model development and validation of computational tools.
\end{itemize}

>>>>

\subsection{Research at UIUC}
Faculty and students in NPRE conduct research in many areas of interest to the nuclear science community. Both graduate and undergraduate  students actively participate and make their own atomic contributions that will someday save the world.
Research programs in Nuclear, Plasma, and Radiological Engineering at the University of Illinois at Urbana-Champaign can be
broadly classified into five areas:
\begin{itemize}
        \item \textbf{Nuclear Power} (reactor physics, thermalhydraulics, fuel cycle, radiation transport, I\&C)
        \item \textbf{Plasma and Fusion} (modeling, plasma-material interactions)
        \item \textbf{Radiological Sciences} (detectors, imaging, health physics, medical applications)
        \item \textbf{Material Science} (nuclear fuels, structural materials)
        \item \textbf{Risk and Policy} (PRA, safety, energy, arms controls, disarmament, security)
\end{itemize}

These research areas are supported by a stellar faculty and world-class facilities, which 
will be briefly described below.

@@

\subsubsection{NPRE Research Groups and Laboratories}
The faculty, pictured in Figure \ref{fig:faculty} support the above areas of 
expertise in the collaborations and facilites discussed below.

\begin{figure}[htbp]
        \begin{center}
                \includegraphics[width=0.75\textwidth]{./images/full.png}
                \includegraphics[width=0.6\textwidth]{./images/associate.png}
                \includegraphics[width=0.6\textwidth]{./images/assistant.png}
                \includegraphics[width=0.3\textwidth]{./images/research.png}
        \end{center}
        \caption{Faculty in Nuclear, Plasma, and Radiological Engineering  at 
        the University of Illinois at Urbana-Champaign.}
        \label{fig:faculty}
\end{figure}

\begin{itemize}
  \item \textbf{Advanced Reactors and Fuel Cycles (ARFC)} - \textit{Dr. Kathryn Huff}\\
  The ARFC group seeks to advance the safety and sustainability of nuclear energy production through improved reactor designs, fuel cycle strategies, and waste management techniques. In the area of advanced reactors, our work focuses on extending current simulation tools with features essential to advanced reactor multiphysics. In the context of the broader nuclear fuel cycle, the ARFC group emphasizes modeling, simulation, and analysis of the global nuclear fuel cycle, with an emphasis on sustainability. A crosscutting theme of our research is an emphasis on advancing methods and software for computational nuclear engineering. Accordingly, the Advanced Reactors and Fuel Cycles group is proud to be affiliated with the University of Illinois National Center for Supercomputing Applications and its Blue Waters computing facility.
  \item \textbf{Virtual Education and Research Laboratory (VERL)} - \textit{Dr. Rizwan Uddin}\\
  The VERL group focuses on the development of innovative numerical methods and their implementation on high performance computing machines. Research efforts center on problems in nuclear engineering, with emphasis on thermal-hydraulics and reactor physics.

@@

  \item \textbf{Laboratory: Multiphase Thermo-fluid Dynamics Lab} - \textit{Dr. Caleb Brooks}\\
  This group performs experiments related to thermal hydraulics and multiphase flow. Phenomena studied include boiling, condensation, critical heat flux, natural circulation, two-phase flow instabilities, bubble dynamics, and two-phase transport. Utilizing advanced instrumentation, data from these experiments are used in model development and validation of computational tools.
  \item \textbf{Laboratory: Nuclear Measurements Laboratory} - \textit{Dr.  Angela DiFulvio}\\ The lab is equipped with a Cf-252 source and a D-T neutron generator with an emission rate of ~1E7 and ~1E8 neutrons/s, respectively. The neutron flux density is well-characterized in energy and intensity employing various instruments, including multisphere spectrometers, ionization chambers, long counters, and scintillators, calibrated to primary reference standards, which enable the detection of neutrons via scattering of protons or via fission of uranium nuclei.
\end{itemize}
